DisCon Kids Pilot

### 2018-11-14 analysis/02_kids.Rmd
clean up analysis folder and add overview file

@@

@@

data <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")))
```

@@

data <- data %>%
  filter(!subid %in% drop)

@@

>>>>

library(lsr)
library(pwr)

@@

files <- dir("../../kids_simple_4cat/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../kids_simple_4cat/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$data$data)
  raw_data <- bind_rows(raw_data, id)
}

data_4cat <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")))

@@

data_6cat <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)"))) %>%
  filter(target1 != "furniture", target1 != "instruments")

data <- bind_rows(data_4cat, data_6cat)

write.csv(data, file="../data/kids_4cat_pilot.data.csv")

data <- read_csv(file="../data/kids_4cat_pilot.data.csv")
```

@@

data %>%
  filter(!subid %in% drop) %>%
  group_by(subage) %>%
  summarise(n = length(unique(subid)))

@@

```{r plot2, fig.width = 8, echo=FALSE, warning = FALSE}
plot2 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, subid, subage) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -subid, -subage) %>%
  group_by(distribution, item, subage) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot2,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(distribution~subage, 
             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", `2` = "2", `3` = "3", `4` = "4"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```

```{r plot5, echo=FALSE, warning = FALSE, cache = TRUE}

plot5 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, subid, target1) %>%
  summarise(correct = mean(correct_target1)) %>%
  gather(item, prop_correct, -distribution, -subid, -target1) %>%
  group_by(distribution, item, target1) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot5,
       aes(x = target1, y=mean, fill=item)) +
  geom_bar(stat='identity') +
 # geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized()+
  guides(fill = F) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  labs(x="category", y= "proportion chosen")
```

``` {r power analysis}
power <- data %>%
  filter(phase == 'test') %>%
  group_by(subid) %>%
  summarise(correct = mean(correct_target1))

t.test(power$correct, mu = 1/3)

cohensD(power$correct, mu = 1/3)

pwr.t.test(d = 0.5127475, sig.level = 0.05, power = .8, type = c("one.sample"))
```
